%====================
% EXPERIENCE A
%====================
\subsection{{Site Reliability Engineer  \hfill Feb 2021 --- Present}}
\subtext{Bayan (Is a privately held Information Technology and consulting company, specializing in large-scale web applications. Bayan has developed many products and services since its establishment. ) \hfill Iran, Tehran}
\begin{zitemize}
\item Created a technical team for the Bayan Enterprise Mail project.
\item Designing and developing a mail engine from scratch using Python programming language, mail protocols and RFCs, different databases, and some other tools.
\item As a Site Reliability Engineer, I create SRE cultures such as creating CI/CDs, incident management processes, and everything that makes the team efficient.
\item Migrated all of Bayan services such as blog.ir, bayanbox.ir from VPS to k8s at minimum downtime.
\item Refactored and upgraded Bayan services to new versions of their stack.
We have 100 r/s on our services.
\end{zitemize}


%====================
% EXPERIENCE B
%====================
\subsection{{Software Engineer  \hfill Apr 2018 --- Feb 2021}}
\subtext{Bale Messenger (Is a Fast and handy Payment and Communication platform built upon a safe messaging and financial system. Bale had 8 million users when I was here and now has 14 million users. ) \hfill Iran, Tehran}

\begin{zitemize}
\item Migrated Bale monolithic server was written by Scala programming language to Microservices with other coworkers and using Go programming language and Kubernetes as container orchestration system and different databases and tools such as Postgres, Redis, Kafka and etc.
\item Implemented, Deployed, and Maintained some services above:
\newline
 Push Notification Service: Processing and sending Bale Messenger's Notifications.
 \newline
 Presence Service: Processing and sending Bale User's status such as online, last seen, typing, etc.
 \newline
 Other services such as Stickers and Settings and some chatbots.
 \item I was also on the engineering recruitment team and had many interviews with new candidates.
\end{zitemize}

